---
title: "SurvivalAnalysis_plotly"
author: "Sarthak"
date: "September 25, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading required libraries
```{r message=FALSE}
library(OIsurv)
library(devtools)
library(plotly)
library(ggplot2)
library(survival)
library(GGally)
```
# Dataset
I am using the `cancer` dataset from the `survival` package. It contains the information about 228 patients with advanced lung cancer from the North Cancer Treatment Group.
This dataset is interesting to me as it has many daily life practical attributes against which lung cancer can be analyzed upon. 

Performance scores rate how well the patient can perform usual daily activities.

List of variables in cancer dataset:

| Variable        | Description    |    
| --------------- | -------------------------------------------------------------------|
| `inst`          | Institution code                                                  |
| `time`          | Survival time in days                                             |
| `status`        | censoring status, 1=censored, 2=dead                              |
| `age`           | age in years                                                      |
| `sex`           | 1=Male, 2= Female                                                 |
| `ph.ecog`       | ECOG performance score (0= good, 5=dead)                          |
| `ph.karno`      | Karnofsky performance score (0=bad, 100=good) rated by physician  |
| `pat.karno`     | Karnofsky performance score as rated by patient                   |
| `meal.cal`      | calories consumed at meals                                        |
| `wt.loss`       | Weight loss in last six months                                    | 

 
```{r message=FALSE}
data(cancer, package = "survival")
attach(cancer)
```

The summary of the dataset looks like this:
```{r}
summary(cancer)
```

Top 6 rows are:
```{r}
head(cancer)
```



# Survival Objects
`survfit` function works on `Surv` objects which are survival types created using `Surv()` function.

Creating surv object:
```{r}
s <- Surv(time, status)
```
The plus-signs identify those observations that are right-censored

Next, we create survival curve using `survfit`. `ggsurv` of `ggplot2` is used here.
```{r}
sf.cancer <- survfit(s ~ 1, data = cancer)
p <- ggsurv(sf.cancer)
ggplotly(p)
```
The graph displays the survival rate over time when all the attributes are considered.

Publish it to plotly:
```{r}
#plotly_POST(p, "Survival vs Time")
```

## Gender wise survival rate
The survival rate over time for males and females is observed here.

Like above, First the surv object is created then the surviva curve is built. And then plotted with the help of ggsurv of ggplot2
```{r}
s1 <- Surv(time, status)
sf.sex <- survfit(s1 ~ sex, data = cancer)
pl.sex <- ggsurv(sf.sex)
ggplotly(pl.sex)
```
This graph is also published to plotly.
```{r}
#plotly_POST(pl.sex, "Gender wise - Survival vs Time")
```
